The History of Social Work Research: A Data Science Perspective

### 2015-02-03 Analysis.Rmd
Final journal mergers
Adds mergers for the following:

1. Convert "The Family" "The Journal of Social Casework" and "Social
Casework" to "Families in Society"
2. Convert "Education in Social Work" to "Children & Schools"

@@

>>>>

#add no authorship indicated
#Anonymous
x.temp <- filter(bwr.df, attributes == "article")
x.temp2 <- filter(bwr.df, attributes == "journal")

x.temp3 <- filter(bwr.df, attributes == "author")
b <- grepl("@", x.temp3$record)

test.case <- filter(bwr.df, attributes == "AU")
auth.name <- filter(test.case, grepl("(Perron,\\sB)", record))

x.temp <- filter(bwr.df, attributes == "KW" | attributes == "KP")

@@

bwr.df$record <- ifelse(bwr.df$record == "The Family", 
                       "Families in Society",
                       ifelse(bwr.df$record == "Journal of Social Casework",
                       "Families in Society",
                       ifelse(bwr.df$record == "Social Casework",
                       "Families in Society",
                        bwr.df$record)))

bwr.df$record <- ifelse(bwr.df$record == "Social Work in Education", 
                       "Children & Schools", 
                        bwr.df$record)
